---
title: "all country"
author: "Gregory Guranich"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{all country}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(fpemdata)
library(fpemreporting)
library(fpemmodeling)
library(ggplot2)
library(grid)
library(gridExtra)
```

## Table of Contents
1. [Introduction](#intro)
2. [Run models](#run)
3. [Plot model results](#plot)
  
## <a name="intro"></a>
## Introduction
In this vignette we will run two models for each country available, one for women in union and another for women not in union. We will use the package default data `fpemdata::contraceptive_use` for this example.
## Make directories for model files, import observed data and global model results
```{r}
# years we will run one country model
first_year = 1970
last_year = 2030

# vector of countries where we have data
divs <- read.csv("Track20Database121819_Pre2013.csv") %>% 
  dplyr::rename(
  "contraceptive_use_any" = "contraceptive_use_all",                           
  "unmet_need_modern" = "unmet_need_for_modern_methods",                        
  "unmet_need_any" ="unmet_need_for_any_method"      
)
write.csv(divs, "Track20_rename.csv")

divs <- divs %>% dplyr::select(division_numeric_code) %>% unique()
popcountdiv <- fpemdata::population_counts
divs <- divs %>% dplyr::filter(division_numeric_code %in% popcountdiv$division_numeric_code)
divnames <- divs %>% 
  dplyr::left_join(fpemdata::divisions) %>%
  dplyr::select(name_country) %>%
  dplyr::pull()
divs <- divs %>% dplyr::pull()


if(!dir.exists("output")) dir.create("output")
# inconsinstent indicator names, FPEM vs UNPD
indicators <- c(
    "unmet_need_any",
    "contraceptive_use_modern",
    "contraceptive_use_traditional",
    "contraceptive_use_any"
    )
indicators_un <- c(
  "unmet",
  "modern",
  "traditional"
)
```

## <a name="run"></a>
## run models
```{r}
# > div
# [1] 580

for(div in divs) {
  run_y <- fpemmodeling::do_1country_run(
    is_in_union = "Y",
    surveydata_filepath = "Track20_rename.csv",
    service_stats = FALSE,
    division_numeric_code = div,
    first_year = first_year,
    last_year = last_year
  )
  run_n <- fpemmodeling::do_1country_run(
    is_in_union = "N",
    surveydata_filepath = "Track20_rename.csv",
    service_stats = FALSE,
    division_numeric_code = div,
    first_year = first_year,
    last_year = last_year
  )
  core_data <- run_y$core_data
  core_data$observations <-
    rbind(run_y$core_data$observations, run_n$core_data$observations)
  samples_all <-
    fpemmodeling::posterior_samples_all_women(
      in_union_posterior_samples = run_y$posterior_samples,
      not_in_union_posterior_samples = run_n$posterior_samples,
      core_data = core_data
    )
  population_counts <- fpemdata::population_counts %>%
    dplyr::filter(division_numeric_code == div)
  results_y <- fpemreporting::fpem_calculate_results(
    posterior_samples = run_y$posterior_samples,
    country_population_counts = population_counts %>%
      dplyr::filter(is_in_union == "Y"),
    first_year = first_year
    )
  results_n <- fpemreporting::fpem_calculate_results(
    posterior_samples = run_n$posterior_samples,
    country_population_counts = population_counts %>%
      dplyr::filter(is_in_union == "N"),
    first_year = first_year
    )
  results_all <- fpemreporting::fpem_calculate_results(
    posterior_samples = samples_all,
    country_population_counts = population_counts,
    first_year = first_year
    )
  reslist <- list(results_y = results_y, 
                  results_n = results_n, 
                  results_all = results_all, 
                  core_data = core_data)
  saveRDS(reslist, file.path("output", paste0("reslist", div, ".rds")))
  print(div)
}

```

## <a name="plot"></a>
## Plot married
```{r}
divnamesordered <- divnames %>% sort()
divsordered <- divs[match(divnamesordered, divnames)]
divs <- divsordered
divnames <- divnamesordered


pl <- list()
i <- 0
for(div in divs){
  i <- i + 1
  reslist <- readRDS(file.path("output", paste0("reslist", div, ".rds")))
  templs <- list()
  pl[[i]] <- fpem_plot_country_results(
    country_results = reslist$results_y,
    observations = reslist$core_data$observations,
    first_year = first_year,
    last_year = last_year,
    is_in_union = "Y",
    indicators = indicators) 
}

pdf("married_track19.pdf", 10,10)
i <- 0
for(divname in divnames) {
  i <- i + 1
  grid.arrange(grobs=pl[[i]], top = textGrob(paste("In-union women",divname)) ,ncol=2)
}
dev.off()
```


# Plot unmarried
```{r}
pl <- list()
i <- 0
for(div in divs){
  i <- i + 1
  reslist <- readRDS(file.path("output", paste0("reslist", div, ".rds")))
  templs <- list()
  pl[[i]] <- fpem_plot_country_results(
    country_results = reslist$results_n,
    observations = reslist$core_data$observation,
    first_year = first_year,
    last_year = last_year,
    is_in_union = "N",
    indicators = indicators) 
}

pdf("unmarried_track19.pdf", 10,10)
i <- 0
for(divname in divnames) {
  i <- i + 1
  grid.arrange(grobs=pl[[i]], top = textGrob(paste("Not-in-union women",divname)) ,ncol=2)
}
dev.off()
```




